\documentclass[ICS, PP, english, final]{ICS_thesis}
\graphicspath{{pics/}{logos/}}


%_________MACROS_________ (optional and customizable - see output)
\input{./include/packages.tex}
\input{./include/macros.tex}
%_______Start_Document______________________________________
\begin{document}


\title{RoboCup SS17}

\student{B.Sc. Tianming Qiu} 			%% your name
\yearofbirth{30.03.1993}	                	%% date of birth
\street{Felsennelkenanger 15}			%% your address
\city{80937, Munich}						%		"
\phone{+49 17643387325}					%% your telephone-no.
\supervisor{Mohsen Kaboli}				%% your supervisor
\start{24.04.2017}						%% start date
\finalrep{24.07.2017}					   	%% final presentation / date

\maketitle



% ________Abstract__________________________________________-
\topmargin5mm
\textheight220mm
\pagenumbering{arabic}
\phantom{u}
\begin{abstract}
RoboCup is a competition for soccer robot held annually and we work on the RoboCup Standard Platform League (SPL) by using humanoid robot NAO, based on the code framework from University of Bremen's team B-Human.

Self-localization is a very important task for NAOs during the match. The action decisions, ball tracking and different team cooperation strategies are dependent on the precise location on the standard soccer field. Self-localization is also related computer vision and statistical signal processing. These topics are the foundations of autonomous robot. So this semester I focus on figuring it out, how does NAO localize itself on the soccer field by cameras and how could it be improved.

The current method in B-Human framework has been continuously developed, verified and implemented for several years. It has been considered as state-of-the-art method which is already very robust and compact. The main idea is to apply particle filter with unscented Kalman filter for each particle to estimate robot pose. But there are still some issues that when robot is walking, some shake noises from camera will cause deviations in visual odometry. PnP pose estimate would be adopted instead of relative distance calculation, which would take all the transform generally into consideration and eliminates the error.
\end{abstract}

% %%%%%%%%%%%%%%%%%%%%% Widmung %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\phantom{u}
\phantom{1}\vspace{6cm}
\begin{center}
%Hier die Widmung oder leer lassen
\end{center}


\pagestyle{fancy}

%%%%%%%%%%%%%%%%%%%Inhaltsverzeichnis%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACTUAL CONTENT OF YOUR WORK %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% Kapitel - externe Dateien zur Ordnung%%%%%%%%%%%%%
\input{./chapters/Introduction.tex}
\input{./chapters/PF.tex}
\input{./chapters/Improvement.tex}
\input{./chapters/Conclusion.tex}

% \appendix
% 	\input{./chapters/Appendix.tex}

%%%%%%%%%%%%%%%%%%Acknoledgments %%%%%%%%%%%%%%%%%%%%%%
%\cleardoublepage
\chapter*{Acknowledgments}
\markright{ACKNOWLEDGMENTS}
First of all, I would like to express my thanks to Prof. Dr. Gordon Cheng and Chair of Cognitive Systems for offering this course and all the hardware equipments.

I would further like to thank our supervisor Mohsen Kaboli for your patient help and many constructive suggestions. You are always willing to share your experiences and give us significant guide. Your office is always open to us. You are strict to us but I really learn a lot from that. Not only the experiment itself also the way how to deliver a presentation.

Also, I would appreciate the help offered by our teaching assistant Zhiliang Wu, who prepared all the lab stuff fur us and wrote detailed tutorial that let me know how to operate NAO step by step. Your careful work make me get start quickly and give me a lot confidence to finish the task. 

I am particularly thankful to my team mate: Yao, Fabian, Zhiyi, Jingjie, and Minkai. We discussed a lot and you always give me some useful supports.

%%%%%%%%%%%%%%%%%%_Abbildungsverzeichnis %%%%%%%%%%%%%%%%%%%%%%
\cleardoublepage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

% %%%%%%%%%%%%%%%%%%_Acronyms and Notations %%%%%%%%%%%%%%%%%%%%%%
 %\cleardoublepage
% \chapter*{Acronyms and Notations}
% \input{./include/acronyms.tex}

%%%%%%%%%%%%%%%%%%Literaturverzeichnis %%%%%%%%%%%%%%%%%%%%%%%%
\cleardoublepage
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{mybib}
\bibliographystyle{unsrt}

%%%%%%%%%%%%%%%%%%%%License %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cleardoublepage
%\chapter*{License}
%\markright{LICENSE}
%This work is licensed under the Creative Commons Attribution 3.0 Germany
%License. To view a copy of this license,
%visit \href{http://creativecommons.org/licenses/by/3.0/de/}{http://creativecommons.org} or send a letter
%to Creative Commons, 171 Second Street, Suite 300, San
%Francisco, California 94105, USA.

\end{document}
